`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-02-03 inst/manuscript/manuscript.rmd
Minor edit to reflect the fact that the repository is public;

Thirdly the code base and development history will, upon publication, be
publicly accessible at
[`https://bitbucket.org/graumannlabtools/flippant`](https://bitbucket.org/graumannlabtools/flippant).

>>>>

Thirdly the code base and development history is publicly accessible at
[`https://bitbucket.org/graumannlabtools/flippant`](https://bitbucket.org/graumannlabtools/flippant).
